Paper Figs

### 2023-10-31 graphs_newt_snakes/Paper_figs.Rmd
making more plots

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "th generation to ", max_gen, "th generation"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
  theme(plot.title = element_text(size=5)) +
    scale_x_discrete(breaks=c('Sims',"F","G","H", "J", "K", "L", "N", "O", "P"), labels=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")) + 
  #  level=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")+
  #xlim(-1.1, 1.1)+
    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutational Variance', 'Coevolution'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),
                      title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))

@@

@@

>>>>

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "th generation to ", max_gen, "th generation"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
  theme(plot.title = element_text(size=5)) +
    scale_x_discrete(breaks=c('Sims',"F","G","H", "J", "K", "L", "N", "O", "P"), labels=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")) + 
  #  level=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")+
  #xlim(-1.1, 1.1)+
    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutational Variance', 'Coevolution'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
  #theme(axis.text.x = element_text(angle = 45, hjust=1))

boxplot_cors_by_gen_col_rep_other3 <- function(file1, file2, file3, title, subt, x_label, y_label, min_gen, max_gen){
 snewt$mean_res = snewt$mean_toxin+snewt$dif
  real_snewt_cor = cor(snewt$mean_toxin, snewt$mean_res)
   file1$snake_newt <- paste0(file1$snake_mu_rate, "_", file1$snake_mu_effect_sd, "_", file1$newt_mu_rate, "_", file1$newt_mu_effect_sd)
   file2$snake_newt <- paste0(file2$snake_mu_rate, "_", file2$snake_mu_effect_sd, "_", file2$newt_mu_rate, "_", file2$newt_mu_effect_sd)
   file3$snake_newt <- paste0(file3$snake_mu_rate, "_", file3$snake_mu_effect_sd, "_", file3$newt_mu_rate, "_", file3$newt_mu_effect_sd)
file <- rbind(file1, file2, file3)

#smallset = file[which(file$gen>=40000 & file$gen<=50000 & file$exp=="Cost Gradent Map" & file$cor_score=="True"),]
file$exp = factor(file$exp, levels=c("Cost Gradent Map No Interaction", "Snake Gradent Map", "Newt Gradent Map"))

  plot <-  ggplot(file[which(file$gen>=min_gen & file$gen<=max_gen),]) +
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, "th generation to ", max_gen, "th generation"))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=factor(sim, level=c('Sims', "F","G","H","J","K","L","N","O","P")), y=as.numeric(mean_newt_pheno_By_mean_snake_pheno), fill=factor(cor_score)))+
  theme(plot.title = element_text(size=5)) +
    scale_x_discrete(breaks=c('Sims',"F","G","H", "J", "K", "L", "N", "O", "P"), labels=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")) + 
  #  level=c("1a's", "2a/2a", "2a/3a", "2a/4a", "3a/2a", "3a/3a", "3a/4a", "4a/2a", "4a/3a", "4a/4a")+
  #xlim(-1.1, 1.1)+
    geom_hline(yintercept=real_snewt_cor, linetype="dashed")+
  facet_wrap(~exp, ncol=1)+
  scale_fill_manual(values =c("darkolivegreen3", "cadetblue2"), labels=c('Low Mutational Variance', 'Coevolution'))+
    labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 18),title =element_text(size=18, face='bold'), legend.text=element_text(size=16), strip.text.x = element_text(size = 20))
  #theme(axis.text.x = element_text(angle = 45, hjust=1))

@@

boxplot_cors_by_gen_col_rep_other3 = boxplot_cors_by_gen_col_rep_other3(file4, file5, file6, title, subt, x_label, y_label, min_gen, max_gen)

ggsave("three_correlation_app.png", plot=boxplot_cors_by_gen_col_rep_other3, height=7, width=11, units=c("in"), dpi=600)

@@

```{r, looking at the realtionship between pop size and phenotype}

whale_gen <- function(file, title, subt, x_label, y_label,min_gen, max_gen, letter){
  #file$rep==rep
  file$snake_GA<-paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)
  file$newt_GA<-paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)
  file$sim_snake_name = NA
  file$sim_newt_name = NA
  #file$sim == "A" | "B" | "C" | "D"
  file[which(file$sim  == "A" | file$sim  == "B" | file$sim  == "C" | file$sim  == "D"), ]$sim_snake_name = paste0("1",letter)
  file[which(file$sim  == "E" | file$sim  == "F" | file$sim  == "G" | file$sim  == "H"), ]$sim_snake_name = paste0("2",letter)
  file[which(file$sim  == "I" | file$sim  == "J" | file$sim  == "K" | file$sim  == "L"), ]$sim_snake_name = paste0("3",letter)
  file[which(file$sim  == "M" | file$sim  == "N" | file$sim  == "O" | file$sim  == "P"), ]$sim_snake_name =  paste0("4",letter)

  file[which(file$sim  == "A" | file$sim  == "E" | file$sim  == "I" | file$sim  == "M"), ]$sim_newt_name =  paste0("1",letter)
  file[which(file$sim  == "B" | file$sim  == "F" | file$sim  == "J" | file$sim  == "N"), ]$sim_newt_name =  paste0("2",letter)
  file[which(file$sim  == "C" | file$sim  == "G" | file$sim  == "K" | file$sim  == "O"), ]$sim_newt_name = paste0("3",letter)
  file[which(file$sim  == "D" | file$sim  == "H" | file$sim  == "L" | file$sim  == "P"), ]$sim_newt_name =  paste0("4",letter)
  file$sim_name = paste0("S:", file$sim_snake_name,"/N:", file$sim_newt_name)

dif <- ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(Newt_pop_size), y=as.numeric(Snake_pop_size), color = dif, shape=factor(rep)))+
  #paste0(snake_mu_rate, "_", snake_mu_effect_sd), shape = paste0(newt_mu_rate, "_", newt_mu_effect_sd), group=T)
  theme(plot.title = element_text(size=5)) +
  scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred", name = "Phenotype Difference (S-N)")+
  scale_shape_discrete(name="Simulation Rep")+
  #labs(colour = color_label) +
  facet_wrap(~fct_reorder(sim_name, sim))+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      # strip.background = element_blank(), 
                      # strip.text.x = element_blank(), 
                      # panel.grid.major = element_blank(), 
                      # panel.grid.minor = element_blank(),
                      # panel.background = element_blank(), 
                      axis.line = element_line(colour = "black"))

return(dif)

min_gen=5000
max_gen=10000
letter="a"
wg1 = whale_gen(GA1_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt="Experiment 1", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
ggsave("Early_Popsize_vs_pheno.png", plot=wg1, height=10, width=10, units=c("in"), dpi=600)
wg1

min_gen=45000
max_gen=50000
wg2 = whale_gen(GA1_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt="Experiment 1", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
ggsave("Late_Popsize_vs_pheno.png", plot=wg2, height=10, width=10, units=c("in"), dpi=600)
wg2

min_gen=5000
max_gen=10000
letter="b"
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt="Experiment 2", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
min_gen=45000
max_gen=50000
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt="Experiment 2", y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)

my_cur_file = mu_b_lit
min_gen=5000
max_gen=10000
letter="c"
experiment_on ="Experiment 2"
whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
min_gen=45000
max_gen=50000
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)

my_cur_file = mu_c_lit
min_gen=5000
max_gen=10000
letter="d"
experiment_on ="Experiment 2"
whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
min_gen=45000
max_gen=50000
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)

my_cur_file = mu_d_lit
min_gen=5000
max_gen=10000
letter="e"
experiment_on ="Experiment 2"
whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
min_gen=45000
max_gen=50000
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)

my_cur_file = v_a_lit
min_gen=5000
max_gen=10000
letter="f"
experiment_on ="Experiment 3"
whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
min_gen=45000
max_gen=50000
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)

my_cur_file = v_b_lit
min_gen=5000
max_gen=10000
letter="g"
experiment_on ="Experiment 3"
whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
min_gen=45000
max_gen=50000
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)

my_cur_file = v_c_lit
min_gen=5000
max_gen=10000
letter="h"
experiment_on ="Experiment 3"
whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
min_gen=45000
max_gen=50000
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)

my_cur_file = v_d_lit
min_gen=5000
max_gen=10000
letter="i"
experiment_on ="Experiment 3"
whale_gen(my_cur_file, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
min_gen=45000
max_gen=50000
whale_gen(mu_a_lit, title="Newt VS Snake Population Size Color=S-N Phenotype", subt=experiment_on, y_label="Snake Population Size", x_label="Newt Population Size", min_gen=min_gen, max_gen=max_gen, letter)
```

```{r, testing the differences between phenotypes and pop sizes for E1, E2, E3}

boxplot_dif_in_phenotype <- function(file, title, subt, x_label, y_label,gen_l, gen_h,lowest){

   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
file$dif = file$Snake_mean_Pheno- file$Newt_mean_Pheno
file$mv_dif <- (log10((file$snake_mu_rate * (file$snake_mu_effect_sd)^2)) - log10((file$newt_mu_rate * (file$newt_mu_effect_sd)^2)))

lowest_mv_gone = file[which(paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)  != lowest & paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)  != lowest),]

data <- lowest_mv_gone[order(lowest_mv_gone$mv_dif), ]
data = data[which(data$generation>=gen_l & data$generation<=gen_h),]
rownames(data) <- 1 : length(rownames(data))

data$order = paste0("(",data$mv_dif,")", data$snake_newt)

data_long <- tidyr::pivot_longer(data, c(Newt_mean_Pheno, Snake_mean_Pheno,dif))

plot <-   
ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
  geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(value),fill=name), alpha=0.3)+
  #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(Snake_mean_Pheno),fill=name),  alpha=0.3)+
  #geom_boxplot(aes(x=as.factor(reorder(order, mv_dif)), y=as.numeric(dif),fill=name), alpha=0.3)+ # group=paste0(mv_dif,snake_newt)
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

#geom_boxplot(data=file[which(file$generation>=45000),],aes(x=(factor(paste0("(",mv_dif,")", snake_newt))), y=as.numeric(dif), group=paste0(mv_dif,snake_newt),  fill="pink"), alpha=0.3)+
#geom_boxplot(data=file[which(file$generation>=100 & file$generation<=5000),],aes(x=(factor(paste0("(",mv_dif,")", snake_newt))), y=as.numeric(dif), group=paste0(mv_dif,snake_newt), fill="green"), alpha=0.3)+

#geom_boxplot(data=file[which(file$generation>=25000 & file$generation<=30000),],aes(x=(factor(paste0("(",mv_dif,")", snake_newt))), y=as.numeric(dif), group=paste0(mv_dif,snake_newt), fill="purple"), alpha=0.3)+

#scale_fill_manual(values = c("purple", "green", "pink" ), labels = c('begin', 'mid', 'end'))+ #values = c("pink", "green", "purple" ),

boxplot_dif_in_phopulationsize <- function(file, title, subt, x_label, y_label, gen_l, gen_h, lowest){

   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
file$dif = file$Snake_pop_size- file$Newt_pop_size
file$mv_dif <- (log10((file$snake_mu_rate * (file$snake_mu_effect_sd)^2)) - log10((file$newt_mu_rate * (file$newt_mu_effect_sd)^2)))

file = file[order(file$mv_dif, file$mv_dif),]
lowest_mv_gone = file[which(paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd)  != lowest & paste0(file$newt_mu_rate, "_", file$newt_mu_effect_sd)  != lowest),]

data <- lowest_mv_gone[order(lowest_mv_gone$mv_dif) , ]
data = data[which(data$generation>=gen_l & data$generation<=gen_h),]
rownames(data) <- 1 : length(rownames(data))

data$order = paste0("(",data$mv_dif,")", data$snake_newt)

data_long <- tidyr::pivot_longer(data, c(Newt_pop_size, Snake_pop_size,dif))

plot <-    ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value),  fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))

boxplot_dif_in_phenotype_less_log <- function(file, title, subt, x_label, y_label,gen_l, gen_h){

   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
file$dif = file$Snake_mean_Pheno- file$Newt_mean_Pheno
file$mv_dif <- (log10(file$snake_mu_rate) - log10(file$newt_mu_rate))

data <- file[order(file$mv_dif) , ]
data = data[which(data$generation>=gen_l & data$generation<=gen_h),]
rownames(data) <- 1 : length(rownames(data))

data$order = paste0("(",data$mv_dif,")", data$snake_newt)
data_long <- tidyr::pivot_longer(data, c(Newt_mean_Pheno, Snake_mean_Pheno,dif))

plot <-   
  ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value), fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))
  return(plot)
}

boxplot_dif_in_phopulationsize_less_log <- function(file, title, subt, x_label, y_label, gen_l, gen_h){

   file$snake_newt <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd)
file$dif = file$Snake_pop_size- file$Newt_pop_size
file$mv_dif <- (log10(file$snake_mu_rate) - log10(file$newt_mu_rate))

file = file[order(file$mv_dif, file$mv_dif),]

data <- file[order(file$mv_dif) , ]
data = data[which(data$generation>=gen_l & data$generation<=gen_h),]
rownames(data) <- 1 : length(rownames(data))

data$order = paste0("(",data$mv_dif,")", data$snake_newt)
data_long <- tidyr::pivot_longer(data, c(Newt_pop_size, Snake_pop_size,dif))

plot <-    ggplot(data_long) +
  ggtitle(title, subtitle = paste0(subt, " gen low ", gen_l, " gen high ", gen_h))+
  xlab(x_label) + ylab(y_label)+
geom_boxplot(aes(x=reorder(order, mv_dif), y=as.numeric(value), fill=name), alpha=0.3)+
    theme(plot.title = element_text(size=5)) +
  scale_alpha(guide = 'none')+
  #labs(fill = " ")+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), 
                      title =element_text(size=8, face='bold'))
  return(plot)
}

gen_l=45000
gen_h=50000
lowest="1e-08_0.005"
title="Phenotype Difference by Mutatinal Varance"
subt="Experiment GA1_lit"
x_label = "Sanke GA - Newt GA"
y_label = "Difference in Phenotype (Snake - Newt)"
boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size (Snake - Newt)"
boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance" 
subt="Experiment mu_a_lit"
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-08_0.005"
boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_b_lit"
x_label = "Simulations" 
y_label = "Difference in Phenotype"
lowest="1e-09_0.0158"
boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_c_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-10_0.05"
boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_d_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-11_0.158"
boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance" 
subt="Experiment v_a_lit" 
x_label = "Simulations" 
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_b_lit"
x_label = "Simulations"
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_c_lit"
x_label = "Simulations" 
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_d_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)

```{r, waht about different points in sim}
gen_l=100
gen_h=5000
lowest="1e-08_0.005"
title="Phenotype Difference by Mutatinal Varance"
subt="Experiment GA1_lit"
x_label = "Sanke GA - Newt GA"
y_label = "Difference in Phenotype (Snake - Newt)"
boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size (Snake - Newt)"
boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance" 
subt="Experiment mu_a_lit"
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-08_0.005"
boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_b_lit"
x_label = "Simulations" 
y_label = "Difference in Phenotype"
lowest="1e-09_0.0158"
boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_c_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-10_0.05"
boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_d_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-11_0.158"
boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance" 
subt="Experiment v_a_lit" 
x_label = "Simulations" 
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_b_lit"
x_label = "Simulations"
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_b_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_c_lit"
x_label = "Simulations" 
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_c_lit, title, subt, x_label, y_label,gen_l, gen_h)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment v_d_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_d_lit, title, subt, x_label, y_label,gen_l, gen_h)

gen_l=25000
gen_h=30000

lowest="1e-08_0.005"
title="Phenotype Difference by Mutatinal Varance"
subt="Experiment GA1_lit"
x_label = "Sanke GA - Newt GA"
y_label = "Difference in Phenotype (Snake - Newt)"
boxplot_dif_in_phenotype (GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size (Snake - Newt)"
boxplot_dif_in_phopulationsize(GA1_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance" 
subt="Experiment mu_a_lit"
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-08_0.005"
boxplot_dif_in_phenotype (mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_a_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_b_lit"
x_label = "Simulations" 
y_label = "Difference in Phenotype"
lowest="1e-09_0.0158"
boxplot_dif_in_phenotype (mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_b_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_c_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-10_0.05"
boxplot_dif_in_phenotype (mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_c_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance"
subt="Experiment mu_d_lit" 
x_label = "Simulations"
y_label = "Difference in Phenotype"
lowest="1e-11_0.158"
boxplot_dif_in_phenotype (mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize(mu_d_lit, title, subt, x_label, y_label,gen_l, gen_h,lowest)

title="Phenotype Difference by Mutatinal Varance" 
subt="Experiment v_a_lit" 
x_label = "Simulations" 
y_label = "Difference in Phenotype"
boxplot_dif_in_phenotype_less_log (v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
title="Populationsize Difference by Mutatinal Varance"
y_label = "Difference in Population Size"
boxplot_dif_in_phopulationsize_less_log(v_a_lit, title, subt, x_label, y_label,gen_l, gen_h)
